---
title: "Introduction to echarty"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to echarty}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Description

**echarty** provides a lean interface between R and Javascript library [ECharts](https://echarts.apache.org/en/index.html). 
We encourage users to follow the original ECharts [API documentation](https://echarts.apache.org/en/option.html) to construct charts with echarty.  
The main command **ec.init** can set multiple native ECharts options to build a chart.  
The benefits - learn a very limited set of commands, and enjoy the **full functionality** of ECharts.

## Package Conventions

pipe-friendly - supports both \%>\% and |>  
commands have three prefixes to help with auto-completion:

- **ec.** for general functions, like _ec.init_
- **ecs.** for Shiny functions, like _ecs.output_
- **ecr.** for rendering functions, like _ecr.band_


## Events

Event handling is usually necessary only in Shiny. See code in
 [eshiny.R](https://github.com/helgasoft/echarty/blob/main/demo/eshiny.R), run as ```demo(eshiny)```.  
echarty has three built-in event callbacks - _click_, _mouseover_,
_mouseout_. All other ECharts
[events](https://echarts.apache.org/en/api.html#events) could be
initialized through ```p$x$capture```. Another option is to use ```p$x$on```
with JavaScript handlers, see code in [ec.examples](https://github.com/helgasoft/echarty/blob/main/R/examples.R).

## Widget **x** parameters

These are _htmlwidget_ and _ECharts_ initialization parameters supported
by echarty. There are code samples for most of them in [ec.examples](https://github.com/helgasoft/echarty/blob/main/R/examples.R):

- capture = event name(s), to monitor events, usually in Shiny
- on = define JavaScript code for event handling, see 
[ECharts](https://echarts.apache.org/en/api.html#echartsInstance.on)
- registerMap = define a map from a geoJSON file, see 
[ECharts](https://echarts.apache.org/en/api.html#echartsInstance.registerMap)
- group = group-name of a chart, see 
[ECharts](https://echarts.apache.org/en/api.html#echartsInstance.group)
- connect = command to connect charts with same group-name, see 
[ECharts](https://echarts.apache.org/en/api.html#echarts.connect)
- locale = EN(default) or ZH, set from _locale_ parameter of _ec.init_, see 
[ECharts](https://echarts.apache.org/en/api.html#echarts.init).
- renderer = _canvas_(default) or _svg_, set from _renderer_ in _ec.init_, see [ECharts](https://echarts.apache.org/en/api.html#echarts.init).
- jcode = custom JavaScript code to execute, set from _js_ parameter of _ec.init_


## R vs Javascript numbering

R indexes are counted starting from 1.  
JS indexes are counted starting from 0.  
echarty supports R-counting in series-encode **x,y,tooltip** and
visualMap-continuous **dimension** when set through _ec.init_.  
All other indexes like _xAxisIndex_, _gridIndex_, etc. need to be set in
JS-counting (for now).

## Code examples

Here is the complete list of sample code **locations**:

- [ec.examples](https://github.com/helgasoft/echarty/blob/main/R/examples.R)
- code in [Github tests](https://github.com/helgasoft/echarty/tree/main/tests/testthat)
- command examples, like in _ec.init_
- Shiny code is in [eshiny.R](https://github.com/helgasoft/echarty/blob/main/demo/eshiny.R), run with ```demo(eshiny)```
- website [gallery](https://helgasoft.github.io/echarty/gallery.html)
and [tutorials](https://helgasoft.github.io/echarty/)
- demos on [RPubs](https://rpubs.com/echarty)
- searchable [gists](https://gist.github.com/helgasoft)
- answers to [Github issues](https://github.com/helgasoft/echarty/issues)


## Global Options

Options are set with R command
[options](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/options).  
Echarty uses the following options:

- echarty.theme = name of theme file, without extension, from folder
```/inst/themes```
- echarty.font = font family name
- echarty.urlTiles = tiles URL template for leaflet maps

```{r opt, echo=FALSE, include=FALSE}
# set/get global options
options('echarty.theme'='jazz') # set
getOption('echarty.theme')      # get
options('echarty.theme'=NULL)   # remove
```
